Analysis of the included studies

### 2023-05-23 analyses/scripts/orv_sys_rev_data_analysis.Rmd
replaced read_rds with readRDS

```{r}
# Load the cleaned data 
long_data <- read_rds(args[1])

#The cleaned data without citations
compact_data_init <- read_rds(args[2])

# The data with citations 
compact_data_with_citation_keys <- read_rds(args[3])

>>>>

```{r rerun_data_cleaning_if_interactive}
#' if this script is being knit interactively, re-run the data cleaning step,
#' and assign the generated cleaned data (in case something has changed) 
#' else if through the terminal, use the 
#' arguments passed through the commandline/make
# knitting_interactively <- isFALSE(is.null(getOption('knitr.in.progress')))
# 
# if (knitting_interactively) {
#   source(here::here("scripts", "orv_models_review_data_cleaning.R"))
# args <- c(
#   here::here("data", "review_data_long_cleaned.rds"),
#   here::here("data", "review_data_compact_cleaned.rds"),
#   here::here("data", "compact_data_with_citation_keys_cleaned.rds")
#   )
# } else {
#  args <- commandArgs(trailingOnly = TRUE)
# }
```

```{r}
args <- c(
  here::here("data", "review_data_long_cleaned.rds"),
  here::here("data", "review_data_compact_cleaned.rds"),
  here::here("data", "compact_data_with_citation_keys_cleaned.rds")
  )
```

```{r}
# Load the cleaned data 
long_data <- readRDS(args[1])

#The cleaned data without citations
compact_data_init <- readRDS(args[2])

# The data with citations 
compact_data_with_citation_keys <- readRDS(args[3])
